Insect venom anaphylaxis: a case - control study of the European Anaphylaxis Registry

### 2019-05-15 analysis/paper/paper.Rmd
figure about ana managment

USe the model from our previous paper
```
```

## Managment
```{r}
testInsectsbinomialTab$management[,-7] %>% knitr::kable()
testInsectsbinomialTab$management[,-7]%>%
  tidyr::gather(value ="Proportion",
         key="Group",
         4:5) %>% 
  ggplot(aes(reorder(variableName,-Proportion),Proportion,fill=Group))+
  geom_bar(stat="identity",position="dodge")+
  theme(axis.text.x=element_text(angle=90))+
  geom_text(aes(y=0.5,label=reorder(signif(pval,2),-Proportion)),angle=90)
```

@@

```{r}
grid.draw(fig_adrenuse1)
```

I matched patients with IVA to a group of similarly severe cases of non-IVA anaphylaxis and evaluated the use of Adrenaline in both of these groups.

>>>>

USe the model from our previous paper

## Managment

@@

```{r adrenuse, fig.cap="**Therapy of IVA cases.** A: General managment methods in IVA and non-IVA. B: Reasons for not administering adrenaline in both IVA and non-IVA cases. C,D,E: Age, sex and severity distribution was matched in cases in both groups to allow for comparable results between IVA and non_IVA cases"}
fig_adrenuse1
```

Patients who underwent IVA significantly less often recived adrenaline treatment than in other adrenaline cases. After adjusting both groups for simmilar age, sex and severity distribution - the difference in adrenaline use was still significant irrespective of the route of administration. Antihistaminic drugs on the other had were given more often in cases of IVA when compared to non-IVA.

IVA was most often treated with corticosteroids and antihistamines (significantly more frequent than in other anaphylaxis cases). On the other hand adrenaline, beta-2 mimetics and oxygen were given more often in non-IVA.

```{r}
ANAscore_matched %>%
        mutate(grouping = recode(grouping,
                                 'insects'='IVA',
                                 'other'='non-IVA'),
               d_522_adren_agg = recode(d_522_adren_agg,
                                       'no'='no adrenaline',
                                       'yes'='adrenaline given') ) %>%
                         group_by(grouping,
                                  #d_AAI_prescribed,
                                  d_522_adren_agg) %>%
                         summarize(n = n()) %>%
  pull(n) %>% 
  matrix(nrow=2) %>% 
  chisq.test() %>% 
```
